Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-12 ms.tex
explain meaning of q1, q2, f1, f2

\begin{equation}
M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
\end{equation}

@@

Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
emissivity power-law indices of the cold and hot components respectively. 
$q_1/q_2$ encodes the relative emission/absorption cross-sections of the two 
dust species, while $f_1$ dictates the relative amounts of each species 
present. Following the convention of FDS99, we choose $\nu_0$=3000 GHz.

@@

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
$T$ by computing only a small set of one dimensional correction factors for the
particular set of $\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 
1.63, 2.82 ..., see Table \ref{tab:global}).

>>>>

\begin{equation}
M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + f_{2}q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
\end{equation}

@@

Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
emissivity power-law indices of the cold and hot components respectively. 
$q_1$ represents the ratio of FIR emission cross section to optical absorption 
cross section for species 1, and similarly $q_2$ for species 2. $f_1$ and 
$f_2$ dictate the relative contributions of the two MBB components to the
combined SED, and can be thought of as encoding the mass fraction of each 
species, although technically $f_1$ ($f_2$) is the optical absorption 
cross-section weighted mass fraction for species 1 (2). Following the 
convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).

@@

%Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
Our color correction approach allows us to predict $\tilde{I}_{\nu_i}$ by 
computing monochromatic flux densities at the central frequency $\nu_{i,c}$ and
then multiplying by factors $b_{\nu_i}(T, \beta)$ which are interpolated off of
a set of precomputed, one-dimensional lookup tables each listing 
$b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the need to interpolate 
in both $\beta$ and $T$ by computing only a small set of one dimensional 
correction factors for the particular set of $\beta$ values of interest (e.g. 
$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}).
